How do changes in ex vary between countries?

### 2022-03-04 draft_paper.Rmd
small edits and added echo=FALSE where missing

Stalling of life expectancy improvements occurred in the UK from 2010 onwards. It was also seen in some other Western European countries. While the reason and severity of this is debated, some also contend the stalling of improvements seen is artefact following an unusual decade of improvement in 2000s (Murphy 2021).

@@

This is a new test using R Studio on Lu's desktop in line 22

@@

```{r}
change_in_ex_selected_countries <- 
  hmd_ex_selected_countries_with_synth %>% 
    group_by(code, x, sex) %>% 
    arrange(year) %>% 
    mutate(delta_ex = ex - lag(ex)) %>% 
    ungroup()

@@

```{r, tab.cap = "Source: HMD"}

@@

We found the only significant change decade-on-decades was for East Germany for females at birth and at aged 65 years...

@@

- **Limitations**: fewer years for comparison in 2010s; comparing different time periods will provide different results.
- Add description of what this needs

>>>>

Stalling of life expectancy improvements occurred in the UK from 2010 onwards. It was also seen in some other Western European countries. While the reason and severity of this is debated, some also contend the stalling of improvements seen is artefact following an unusual decade of improvement in 2000s (e.g. Murphy 2021).

@@

@@

```{r, echo=FALSE}
change_in_ex_selected_countries <- 
  hmd_ex_selected_countries_with_synth %>% 
    group_by(code, x, sex) %>% 
    arrange(year) %>% 
    mutate(delta_ex = ex - lag(ex)) %>% 
    ungroup()

@@

The table below shows average improvements by decade for England and Wales (standard error).

```{r, echo=FALSE, tab.cap = "Source: HMD"}

@@

We found the only significant change decade-on-decades was for East Germany for females at birth and at aged 65 years. This is consistent with existing literature in this area, showing the convergence of life expectancy for females in East and West Germany following reunification.

@@

- **Limitations**: fewer years for comparison in 2010s for some nations; comparing different time periods will provide different results e.g. New Labour years in E&W.
